An Imaging Search for Circumstellar Companions of Sirius B

### 2021-07-31 paper/paper.tex
update paper

\title{A Search for Circumstellar Companions of Sirius B}

\shortauthors{Lucas et al.}

@@

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}. Despite the high sensitivity of our observations, we do not detect any companions around Sirius B, which is consistent with previous studies. These observations showcase that for nearby faint targets direct imaging is ultimately limited by background noise more than contrast.
\end{abstract}

@@

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. The process required to image a planet is daunting, however. The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}. In addition, the close angular separation of planets makes it difficult to detect them over the diffraction pattern of the star and other noise sources. In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.

Typical targets for imaging are nearby young stars; the close proximity decreases the projected separation of the inner working angle (IWA) of the instrument, allowing closer investigation, and younger exoplanets are hotter and therefore the contrast is reduced. Another way to reduce contrast would be to reduce the luminosity of the star, which is not possible during the main-sequence (MS) lifetime of a star but is possible in the latest stages of stellar evolution. When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) reach the end of their lifetimes, they become white dwarfs and begin cooling, which reduces their luminosity by a factor of $10^3-10^4$ compared to their progenitors. The faintness, broad spectral lines, and  expanded orbits, as we will discuss below, all make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.

White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars. \cite{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the red giant (RGB) phase. Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible. During the asymptotic giant (AGB) phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. Overall, the probability of discovering a \textit{first-generation} planet around a white dwarf is low, but there are potential methods for \textit{second-generation} planets to exist after the violent RGB and AGB phases.

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by looking for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history. Of the $\sim$100 white dwarfs they studied, no companions were found. The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38. Eventually this excess was determined to be from a dust disc \citep{telesco_observations_1990}, with the current interpretation associating the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.

To date, there has been no direct images of an exoplanet around a white dwarf. The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

@@

Some of the first modern imaging studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}). \citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}). \citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

In this work we report our study of Sirius B using direct images from Keck/NIRC2. \autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes which have to deal with extra scattering and diffraction from the atmosphere.

We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the -1.35 K-band magnitude diffraction patterns from Sirius A would sweep into the field of view (FOV) of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowich_performance_2000} was not designed to accommodate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the WFS. We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius B by $\sim$6 magnitudes. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with QACITS, but again the scattered light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.

@@

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF. The co-registered frames are then shifted to the center of the FOV. Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch. With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo \citep{lucas_nirc2_2021}.

@@

A common problem when using subspace-driven ADI algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). In our analysis we employ the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without having to settle on the number of components ahead of time. For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10. We chose 10 as the max number of components because we saw a dramatic dropoff in contrast sensitivity after the first few components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.

@@

\begin{figure*}[t]
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The companion mass values are interpolated from the AMES-Cond grid. The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
    \label{fig:contrast}
\end{figure*}

We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}. For the first two epochs full-frame median subtraction had the best contrast at all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).

In these images there is not \textit{consistent} or overwhelming evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} from the center. The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.

@@

In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR. While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets. In this work we present high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}. In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.

In recent years improving contrast and inner working angle were the dominant parameters of interest. Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the sky background than the speckle noise. Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}. This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.

@@

\input{sections/adi_results_full}

@@

\begin{deluxetable}{ccc}[h!]
    \tablecaption{Provisional astrometry for blobs of interesest from each epoch. The uncertainties are represented in parantheses and are derived from the FWHM of the PSF from each epoch.
    \label{tbl:astrometry}}
    \tablehead{
        \colhead{Date observed} &
        \colhead{offset (\unit{\milliarcsecond})} &
        \colhead{PA (\unit{\degree})}
    }
    \startdata
    2020-02-04 & $114\pm 40$ & $-115\pm 20$  \\
    2020-11-21 & $121\pm 38$ & $-119\pm 18$  \\
    2020-11-28 & $114\pm 41$ & $-113\pm 21$  \\
    \enddata
\end{deluxetable}

\begin{figure}[h!]
    \centering
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components. Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
\end{figure}

\begin{figure}[h!]
    \centering
    \plotone{orbit_corner}
    \caption{Corner plot of the marginal posteriors from the OFTI samples.}
\end{figure}

>>>>

\title{An Imaging Search for Circumstellar Companions of Sirius B}

\shorttitle{An Imaging Search for Circumstellar Companions of Sirius B}
\shortauthors{Lucas et al.}

@@

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities and sub-AU separations, reaching $\sim$\qty{3.5}{\jupitermass} at $\sim$\qty{0.25}{\au} down to a sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}. We do not detect any companions around Sirius B, consistent with previous studies. Our observations are ultimately limited by the sky background more than contrast or separation, which is promising for future imaging studies of nearby faint targets.
\end{abstract}

@@

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. The process required to image a planet is daunting, however. The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}. The infrared is where blackbody emission from exoplanets peaks, while simultaneously being well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible. In addition, the close angular separations of planets makes it difficult to detect them over the diffraction pattern of their host and other noise sources.

Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a closer projected separation, allowing closer investigation, and younger exoplanets are hotter and therefore brighter, reducing the contrast. Another way to reduce contrast would be to make the star fainter, which is precisely what happens in the latest stages of stellar evolution during the white dwarf cooling sequence. When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will eventually exit the main-sequence (MS) and expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase, potentially engulfing planets within the star's roche limit. Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits. Once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor. The faintness broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.

White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase. Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to enter the system after the violent RGB and AGB phases \citep{perets_second_2010}.

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by searching for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. They found no companions around the $\sim$100 white dwarfs they studied. The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38. Eventually this excess was determined to be from a dust disk \citep{telesco_observations_1990} which is indicative of the planetary formation history. The current interpretation associates the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.

To date, there has been no direct images of an exoplanet around a white dwarf, although a planetary-mass brown dwarf with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit was imaged around a single white dwarf (WD 0806-661B) using Spitzer \citep{luhman_discovery_2011}. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

@@

The first modern imaging study searching for companions around Sirius B was \citet{schroeder_search_2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchner_search_2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}). \citet{bonnet-bidaud_adonis_2008} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemer_sirius_2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmann_piercing_2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

In this work we report direct images of Sirius B with Keck/NIRC2. \autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes. We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowich_performance_2000} was not designed to accommodate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the WFS. We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius A by $\sim$6 magnitudes. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with QACITS, but again the scattered light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.

@@

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to reach floating-point centroid accuracy.

The co-registered frames are then shifted to the center of the FOV. Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch. With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yelda_improving_2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo\footnote{\citealt{lucas_nirc2_2021}}.

@@

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10. We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components. In our analysis we employ the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.

@@

\begin{figure*}[t]
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The companion mass values are interpolated from the AMES-Cond grid. The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line. The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
    \label{fig:contrast}
\end{figure*}

We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}. For the first two epochs full-frame median subtraction had the best contrast at almost all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. The innermost annulus from this algorithm has greater than 1 contrast and is not shown. The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).

The reduced images do not show consistent or overwhelming evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} from the center. The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.

@@

In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR. While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets. In this work we present high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}. In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results. This non-detection is compelling for revising occurrence rates of second-generation planets and debris disks around white dwarfs.

In recent years improving contrast and inner working angle were the dominant parameters of interest. Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the sky background than the speckle noise. Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}. This means potentially reach sub-Jupiter sensitivities around young systems ($\lesssim$\qty{300}{\mega\year}) and $<$\qty{10}{\jupitermass} sensitivities around moderate age systems ($\lesssim$\qty{7}{\giga\year}) for 10s-100s of targets without coronagraphy or extreme AO.

@@

\input{sections/adi_results}

@@

We found multiple interesting blobs in the reduced data that were not statistically significant. Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions. We began by estimating the astrometry of the blobs by eye in reduced data (\autoref{tbl:astrometry}, \autoref{fig:prov-orbit}). We tried simulating $10^4$ orbits via rejection sampling with OFTI but failed to constrain all three points with any one orbit. Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.

\begin{deluxetable}{ccc}[h!]
    \tablecaption{Provisional astrometry for blobs of interest from each epoch. The separation and offset are in relation to Sirius B. The uncertainties are derived from the FWHM of the PSF from each epoch.
    \label{tbl:astrometry}}
    \tablehead{
        \colhead{Date observed} &
        \colhead{offset (\unit{\milliarcsecond})} &
        \colhead{PA (\unit{\degree})}
    }
    \startdata
    2020-02-04 & $114\pm 40$ & $-115\pm 20$  \\
    2020-11-21 & $121\pm 38$ & $-119\pm 18$  \\
    2020-11-28 & $114\pm 41$ & $-113\pm 21$  \\
    \enddata
\end{deluxetable}

\begin{figure}[h!]
    \centering
    \figurenum{13}
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components. Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
    \label{fig:prov-orbit}
\end{figure}
